Performance-portable Parallel Programming in Computer Science Education with Kokkos

### 2020-01-23 src/2.GenericProgramming.tex
Touched up final paragraph

Both examples provide the semantic information on what to parallelize, however, they do not provide information on how to map the parallel execution on modern parallel architectures. In order to define what further information is needed to express concurrency on modern computer architectures, it is important to define an abstract machine model first.

>>>>

Kokkos takes the declarative approach. For the developers of our large scientific applications, this is appealing because it allows them to express their algorithms in one way, and rely on Kokkos to map that intent effectively to a variety of architectures. For students this is appealing because they\'re unlikely to have expertise in these architectures. For an educator looking for an implementation vehicle with which to teach students about parallelism, the declarative model eliminates the burden of reimplementing exercises as computer labs and dominant architectures change. For a declarative model to make sense, the educator should know something about the abstract execution model being used to ensure performance portability. Depending on the nature of the course, this could be mostly hidden from students, or discussed in detail.
